---
title: "Problem 5.9"
author: "Yuwen Tan"
output: html_document
---

### (a) Estimate the population mean of medv
```{r}
library(MASS)
mean(Boston$medv)
```

### (b) Estimate the standard error
```{r}
sd(Boston$medv)/sqrt(length(Boston$medv))
```

### (c) Estimate the standard error by bootstrap
```{r}
library(boot)
mean.fn <- function(data,index) {
  return(mean(data[index]))
}
set.seed(1)
Boot <- boot(Boston$medv,mean.fn,R=1000)
Boot
```

The result is close to the answer in (b), but bootstrap is a little larger.

### (d) Confidence interval
```{r}
Boot$t0-2*sd(Boot$t)
Boot$t0+2*sd(Boot$t)
t.test(Boston$medv)
```

These results are close, but bootstrap is a little larger.

### (e) Estimate the population median of medv
```{r}
median(Boston$medv)
```

### (f) Estimate the standard error by bootstrap
```{r}
median.fn <- function(data,index) {
  return(median(data[index]))
}
set.seed(1)
boot(Boston$medv,median.fn,R=1000)
```

### (g) Estimate the tenth percentile of medv
```{r}
quantile(Boston$medv,0.1)
```

### (h) Estimate the standard error by bootstrap
```{r}
quantile.fn <- function(data,index) {
  return(quantile(data[index],0.1))
}
set.seed(1)
boot(Boston$medv,quantile.fn,R=1000)
```