---
title: "Problem 2.9"
author: "Yuwen Tan"
output: html_document
---


### (a) Get predictor types
```{r}
Auto <- read.table("Auto.data",header = T,na.strings = "?")
Auto <- na.omit(Auto)
summary(Auto)
```

We can see that qualitative predictors is name, and others are quantitative predictors.

### (b) Find the range for each quantitative predictor
```{r}
ranges <- matrix(0,8,2)
for (i in 1:8) {
  ranges[i,] <- t(range(Auto[,i]))
}
ranges <- data.frame(ranges)
rownames(ranges) <- names(Auto)[1:8]
colnames(ranges) <- c("low","high")
ranges
```

### (c) Find the mean and standard deviation for each quantitative predictor
```{r}
stats <- matrix(0,8,2)
for (i in 1:8) {
  stats[i,1] <- mean(Auto[,i])
  stats[i,2] <- sd(Auto[,i])
}
stats <- data.frame(stats)
rownames(stats) <- names(Auto)[1:8]
colnames(stats) <- c("mean","std")
stats
```

### (d) Redo part (c) after removing 10th through 85th observations
```{r}
Auto.sub <- Auto[-c(10:85),]
stats <- matrix(0,8,2)
for (i in 1:8) {
  stats[i,1] <- mean(Auto.sub[,i])
  stats[i,2] <- sd(Auto.sub[,i])
}
stats <- data.frame(stats)
rownames(stats) <- names(Auto.sub)[1:8]
colnames(stats) <- c("mean","std")
stats
```

### (e) Investigate some relationships
```{r}
pairs(Auto)
par(mfrow=c(2,2))
plot(Auto$cylinders,Auto$mpg)
plot(Auto$horsepower,Auto$mpg)
plot(Auto$weight,Auto$mpg)
plot(Auto$year,Auto$mpg)
```

### (f) From the panel shown above, those 4 variables could be helpful to forecast mpg.