---
title: "Problem 2.10"
author: "Yuwen Tan"
output: html_document
---


### (a) Load the Boston data
```{r}
library(MASS)
show(?Boston)
```

### (b) Make pairwise scatterplots
```{r}
pairs(Boston)
```

### (c) From the scatterplots, rad and tax seem to be some related predictors. Higher rad or tax may lead to higher crime.

### (d) Find the ranges for some predictors
```{r}
ranges <- matrix(0,3,2)
ranges[1,] <- t(range(Boston$crim))
ranges[2,] <- t(range(Boston$tax))
ranges[3,] <- t(range(Boston$ptratio))
ranges <- data.frame(ranges)
rownames(ranges) <- c("crime rates","tax rates","pupil-teacher rates")
colnames(ranges) <- c("low","high")
ranges
```

It is clear that crime rates and tax rates differ a lot, while pupil-teacher rates have a relatively small range.

### (e) Total number of suburbs bound the Charles river
```{r}
sum(Boston$chas)
```

### (f) Median pupil-teacher ratio
```{r}
median(Boston$ptratio)
```

### (g) The suburb with the lowest median value of owner-occupied homes
```{r}
Boston.lowMedv <- Boston[which(Boston$medv==min(Boston$medv)),]
num <- length(Boston.lowMedv[,1])
for (i in 1:length(names(Boston))) {
  Boston.lowMedv[c(num+1,num+2),i]<-range(Boston[,i])
}
rownames(Boston.lowMedv)[c(num+1,num+2)] <- c("low","high")
Boston.lowMedv
```

### (g) Number of suburbs regarding rooms per dwelling
Number of suburbs with rm more than 7:
```{r}
sum(Boston$rm>7)
```

Number of suburbs with rm more than 8:
```{r}
sum(Boston$rm>8)
```

Details of those with rm more than 8:
```{r}
Boston.highRm <- Boston[Boston$rm>8,]
num <- length(Boston.highRm[,1])
for (i in 1:length(names(Boston))) {
  Boston.highRm[c(num+1,num+2),i]<-range(Boston[,i])
}
rownames(Boston.highRm)[c(num+1,num+2)] <- c("low","high")
Boston.highRm
```