---
title: "Problem 3.9"
author: "Yuwen Tan"
output: html_document
---

### (a) Scatterplot matrix
```{r}
Auto <- read.table("Auto.data",header = T,na.strings = "?")
Auto <- na.omit(Auto)
attach(Auto)
pairs(Auto)
```

### (b) Correlations
```{r}
cor(Auto[colnames(Auto) != "name"])
```

### (c) Multiple linear regression
```{r}
lm.fit <- lm(mpg~.,data = Auto[colnames(Auto) != "name"])
summary(lm.fit)
```

(i) From the overall R-square and p-value, there is a relationship between the predictors and the response.
(ii) Displacement, weight, year and origin are predictors with a statistically significant relationship to the response.
(iii) The coefficient for year is 0.750773, which suggests that newer cars tend to have higher mpg.

### (d) Disgnostic plots
```{r}
par(mfrow=c(2,2))
plot(lm.fit)
```

* The Q-Q plot actually shows that there are some unusually large outliers.
* The residual-vs-leverage plot shows that all residuals have low Cook's distance, with only one point having relatively high leverage.

### (e) Refit with interaction effects
```{r}
lm.fit <- lm(mpg~weight*year,data = Auto)
summary(lm.fit)
```

The interation of weight and year seems to be statistically significant.

### (f) Tranformation of the variables
```{r}
lm.fit <- lm(mpg~poly(weight,2),data = Auto)
summary(lm.fit)
```

This also looks like a acceptable model, using weight and squared weight as the predictors.