---
title: "Problem 3.15"
author: "Yuwen Tan"
output: html_document
---

### (a) Simple linear regression models
```{r}
library(MASS)
predictor <- names(Boston)
predictor <- predictor[-1]
coef_uni <- c()
for (x in predictor) {
  lm.fit <- lm(Boston$crim~Boston[,x])
  show(x)
  show(summary(lm.fit))
  coef_uni <- c(coef_uni,coef(lm.fit)[2])
}
names(coef_uni) <- predictor
```

Many predictors have statistically significant association with the response. These predictors are zn, indus, nox, rm, age, dis, rad, tax, ptratio, black, lstat, medv.

Take lstat as an exmaple.
```{r}
lm.fit <- lm(crim~lstat, data = Boston)
plot(Boston$lstat,Boston$crim)
abline(lm.fit,col="red")
par(mfrow=c(2,2))
plot(lm.fit)
```

### (b) A multiple regression model
```{r}
lm.fit <- lm(crim~.,data = Boston)
summary(lm.fit)
coef_multi <- coef(lm.fit)[-1]
```

In this model, only dis and rad are very significant. Many predictors are not as significant as they are for models in (a).

### (c) Compare regression models
```{r}
plot(coef_uni,coef_multi,xlab="Univariate Coefficient",ylab="Multivariate Coefficient")
text(coef_uni,coef_multi,names(coef_uni),col = "red",cex = 0.5,pos = 4)
```

### (d) Non-linear association
```{r}
predictor <- predictor[-3]
for (x in predictor) {
  lm.fit <- lm(Boston$crim~poly(Boston[,x],3))
  show(x)
  show(summary(lm.fit))
}
```
