---
title: "Problem 3.8"
author: "Yuwen Tan"
output: html_document
---

### (a) Simple linear regression
```{r}
Auto <- read.table("Auto.data",header = T,na.strings = "?")
Auto <- na.omit(Auto)
lm.fit <- lm(mpg ~ horsepower, data = Auto)
summary(lm.fit)
```

(i) From the R-square and p-value shown above, ther is a relationship between the predictor horsepower and the response mpg.
(ii) The t-value for the coefficient of horsepower is -24.49, so the relationship is pretty strong.
(iii) The coefficient estimate negative, meaning the relationship is negative.
(iv) See the codes and outputs below:
```{r}
predict(lm.fit,data.frame(horsepower=8),interval="confidence")
predict(lm.fit,data.frame(horsepower=8),interval="prediction")
```

### (b) Plot the linear regression
```{r}
plot(Auto$horsepower,Auto$mpg)
abline(lm.fit,lwd=3,col="red")
```

### (c) Diagnostic plots of the linear regression
```{r}
par(mfrow=c(2,2))
plot(lm.fit)
```

* From the residual plot, horsepower may be not linear related to mpg.
* From the Q-Q plot, errors are normally distributed.
* From the scale-location plot, the homoscedasticity assumption is held.
* From the residual-vs-leverage plot, no points have large Cook's distance.