---
title: "Problem 3.13"
author: "Yuwen Tan"
output: html_document
---
#### Preparation
```{r}
set.seed(1)
```

### (a) Create x
```{r}
x <- rnorm(100)
```

### (b) Create eps
```{r}
eps <- rnorm(100)
```

### (c) Generate y
```{r}
y <- -1+0.5*x+eps
length(y)
```

In this liner model, /beta_0 is -1, /beta_1 is 0.5.

### (d) Scatterplot
```{r}
plot(x,y)
```

The relationship between x and y is not clear from the plot, but somehow it shows that higher x leads to higher y.

### (e) Fit a least squares linear model
```{r}
lm.fit <- lm(y ~ x)
summary(lm.fit)
```

The estimates are very close to the real values of coefficients.

### (f) Display the regression line
```{r}
plot(x,y)
abline(lm.fit, col = "red")
legend("bottomright",c("(x,y)","regression line"),col=c("black","red"),pch=c("o",""),lty=0:1)
```

### (g) Fit a polynomial regression model
```{r}
lm.fit.quad <- lm(y ~ poly(x,2))
summary(lm.fit.quad)
```

The polynomial model has slightly higher R-square, but the quadratic term is not significant. SO the model may not perform better.

### (h) Refit linear model with less noise
```{r}
x <- rnorm(100)
eps <- rnorm(100,sd=0.1)
y <- -1+0.5*x+eps
lm.fit.less <- lm(y ~ x)
summary(lm.fit.less)
plot(x,y)
abline(lm.fit.less, col = "red")
legend("bottomright",c("(x,y)","regression line"),col=c("black","red"),pch=c("o",""),lty=0:1)
```

The linear model seems to fit even better.

### (i) Refit linear model with more noise
```{r}
x <- rnorm(100)
eps <- rnorm(100,sd=10)
y <- -1+0.5*x+eps
lm.fit.more <- lm(y ~ x)
summary(lm.fit.more)
plot(x,y)
abline(lm.fit.more, col = "red")
legend("bottomright",c("(x,y)","regression line"),col=c("black","red"),pch=c("o",""),lty=0:1)
```

The linear model does not fit so well in this case.

### (j) Confidence intervals
```{r}
confint(lm.fit)
confint(lm.fit.less)
confint(lm.fit.more)
```

Clearly, when the noise is smaller, the confidence interval is narrower.