---
title: "Problem 3.10"
author: "Yuwen Tan"
output: html_document
---

### (a) Multiple linear regression
```{r}
library(ISLR)
lm.fit <- lm(Sales ~ Price+Urban+US, data = Carseats)
```

### (b) Coefficient interpretation
```{r}
summary(lm.fit)
contrasts(Carseats$Urban)
contrasts(Carseats$US)
```

Note that Urban and US are both qualitatice, with denote "Yes" as 1 and "No" as 0.

### (c) The model

Sales = 13.043469 - 0.054459*Price - 0.021916 (if Urban) + 1.200573 (if US)

### (d) Significant predictors

From the p-values shown above, we can reject the null hypothesis for Price and USYes.

### (e) Refit a smaller model
```{r}
lm.refit <- lm(Sales ~ Price+US, data = Carseats)
```

### (f) Compare two models
```{r}
summary(lm.fit)
summary(lm.refit)
```

Two models have similar results, but the model in (e) has higher F-statistic and higher adjusted R-square, a little bit better than the model in (a).

### (g) Confidence intervals for the coefficients
```{r}
confint(lm.refit)
```

### (f) Diagnostic plots
```{r}
par(mfrow=c(2,2))
plot(lm.refit)
```

* There are not clear outliers.
* There are no high leverage observations.